Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-09 ms.tex
Finished section on logistic regression.  Citation on effect regularization parameter on training time is needed.

%-------------------------------------------------%
\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
%-------------------------------------------------%
\todo{ Logisitic regression (LR) is a linear classifier, which finds
  the optimal hyperplane between two classes of data points.  In our
  case, the two classes are lens and non-lens containing images.  The
  data points are the HOG feature vectors transformed from the
  training set data.  Each point occupies an N-dimensional space,
  where N is the length of the HOG vector.  In fitting for the best
  hyperplane, we must regularize the model to prevent overfitting,
  adding an additional parameter in our parameter search,
  regularization parameter $C_\text{LogReg}$.

Regularization minimizes the a cost function with respect to ....
Larger values of $C_\text{LogReg}$ correspond to increasing model
complexity.  Figure~\ref{fig:regularization} shows the accuracy of a
model for selected HOG parameters as a function of the regularization
parameter, $C_\text{LogReg}$.

The performance of a model can be measured as either the score of the
model on a test set, or some other metric, such as the area under the
Receiver Operating Characteristic curve (see Section~\ref{sec:ROC}).

The $C_{LogReg}$ will also increase the training time, \todo{since
  larger coefficients correspond to a more singular matrix}.  We
discuss the score and train time dependence on logistic regression
coefficient in Section\ref{sec:regularization}.
}
% Regularization coefficient:
% http://openclassroom.stanford.edu/MainFolder/DocumentPage.php?course=MachineLearning&doc=exercises/ex5/ex5.html

>>>>

%-------------------------------------------------%
\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:LR}
%-------------------------------------------------%
The problem of detecting gravitational lenses in images falls
under the general category of \em{classification} in machine
learning. In general the task is to find a function that
assigns data points $x$ to one of two or more classes, denoted
by the class label $y$.  This is
equivalent to specifying a decision boundary, or decision
boundaries between the classes in the space of the data points.
(Compare this to
\em{regression} in which the task is to find a function 
$y=f(x)$, where $y$ is a continuous, rather than discrete,
variable.) In our case, we have two classes: lens and
non-lens containing images, and the data points $x$ are the
HOG feature vectors transformed from the training set data.
In this paper we use the Logisitic Regression (LR)
algorithm, for which the decision boundary is a hyperplane .
(The equivalent in the regression setting would be linear
regression.) In LR we determine the optimal hyperplane by
minimizing the objective function
\begin{equation}
\label{log_reg_objective}
L(A,b) = \sum_i \log \left[1 + \exp \left(-y_i (A \cdot x_i + b) \right) \right]
\end{equation}
where $x_i$ is a data point (HOG feature vector), $y_i$ is the
known label for that data point ($1$ for a lens containing
image, $-1$ for a non-lens containing), and $A$ and $b$ are
the parameters of the hyperplane. Eq. \ref{log_reg_objective}
is to be minimized with respect to $A$ and $b$.
Other more complicated machine learning algorithms exist which
do not necessarily produce a linear decision boundary, such as
Support Vector Machines (SVM), Random Forests, and Neural Networks.
training set data \citep{hastie_09}.

The HOG feature vectors in this paper can be very high-dimensional.
When dealing with high-dimensional data, where the number of
dimensions becomes comparable to the number of data points,
overfitting can become an issue. (An example of an extreme case
of overfitting would be if you fit a degree $n$ polynomial to $n$
points.  The polynomial would simply wiggle so that it goes
through every point, and would have no predictive power if you
tried to interpolate or extrapolate.) In machine learning,
overfitting is avoided using different \em{regularization}
techniques. A common choice for logistic regression is to
add a penalty term to Eq. \ref{log_reg_objective}
\begin{equation}\ref{log_reg_regularized}
L_\text{Reg}(A,b,C_\text{LogReg}) = L(A,b) + \frac{1}{2C_\text{LogReg}} \|A\|
\end{equation}
where the norm $\|A\|$ is typically taken as either the
sum of squares of the coefficients ($L_2$ norm) or the sum
of absolute values of the coefficients ($L_1$ norm).  In this
paper we use the former.

The amount of regularization is
controlled by the parameter $C_\text{LogReg}$:
larger values of $C_\text{LogReg}$ correspond to increasing model
complexity.  If $C_\text{LogReg}$ is too large then the model will
overfit, and if it is too small the model will underfit.
To determine whether a model is overfit or underfit, the model is
trained, (i.e. Eq. \ref{log_reg_regularized} is minimized), on a
subset of the data called the \em{training set} and its performance
(goodness of fit) is evaluated both on the the training set and
a set of hold-out data called the \em{test set} that was not used
in constructing the model.
Figure~\ref{fig:regularization} shows the performance of a
model for selected HOG parameters as a function of the regularization
parameter, $C_\text{LogReg}$, for both the training and the test set.
(The performance can be measured by the accuracy, i.e. percent of
images correctly classified, or by some other metric,
such as the area under the
Receiver Operating Characteristic curve (see Section~\ref{sec:ROC}).)

When $C_\text{LogReg}$ is small, the performance of the model improves
with increasing $C_\text{LogReg}$ on both the training and test set,
meaning that $C_\text{LogReg}$ is
still in the underfitting regime. Eventually the performance on the
test set reaches a maximum and starts to decrease, even while the
performance on the training set continues to increase.  This means
that the model is no longer generalizing well and is starting to
overfit. The optimal $C_\text{LogReg}$ occurs when the performance
of the test set is at its maximum; this is the value of $C_\text{LogReg}$
that should be used in the final model.

In practice, there is something of a trade-off between accuracy and
computational resources because a larger value of $C_\text{LogReg}$
will also increase the training time, since a larger $C_\text{LogReg}$
corresponds to a less constrained parameter space being searched
\todo{(citation needed)}.
We discuss the performance and training time dependence on $C_\text{LogReg}$
in Section\ref{sec:regularization}.
